---
title: "MS2"
author: "Likhitha Mandapati"
date: "2023-04-30"
output: pdf_document
toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


\newpage
```{r include=FALSE}

library(tidyverse)
library(lubridate)
library(ggplot2)
library(cowplot)
library(ggpubr)
library(readr)
library(gridExtra)
library(dplyr)
library(tidyr)
library(knitr)
library(MASS)
library("car")
library(lme4)
library(lmerTest)
library(lattice)
library(sjPlot)
library(corrplot)
library(Matrix)
library(arm)  
library(lme4)
library(TMB)
```

```{r include=FALSE}

Df <- read.csv("/Users/student/Documents/Spring 23/STAT/Team3_MS2/Affective_Driving_Dataset_N21.csv")

```


```{r include=FALSE, warning=FALSE}
data <- Df %>%
  group_by(P_ID,Trip.,Day.,Trip_Period) %>%
  summarise(
    Weather.mean = round(mean(Weather, na.rm = T),3),
    Day_Type = unique(Day_Type),
     HR_Raw.mean = round(mean(HR_Raw, na.rm = T),3),
     Speed.mean = round(mean(Speed, na.rm = T),3),
     ATP.mean = round(mean(ATP, na.rm = T),3),
     Accel_Energy.mean = round(mean(Accel_Energy, na.rm = T),3),
     Rot_Energy.mean = round(mean(Rot_Energy, na.rm = T),3),
     JF.mean = round(mean(JF, na.rm = T),3),
     State_Anxiety.mean = round(mean(State_Anxiety, na.rm = T),3),
     MD.mean = round(mean(MD, na.rm = T),3),
     PD.mean = round(mean(PD, na.rm = T),3),
     TD.mean = round(mean(TD, na.rm = T),3),
     P.mean = round(mean(P, na.rm = T),3),
     E.mean = round(mean(E, na.rm = T),3),
     F.mean = round(mean(F, na.rm = T),3),
     Trait_Anxiety.mean = round(mean(Trait_Anxiety, na.rm = T),3),
     B5A.mean = round(mean(B5A, na.rm = T),3),
     B5C.mean = round(mean(B5C, na.rm = T),3),
     B5E.mean = round(mean(B5E, na.rm = T),3),
     B5N.mean = round(mean(B5N, na.rm = T),3),
     B5O.mean = round(mean(B5O, na.rm = T),3),
     Gender = unique(Gender)
  )
```


```{r include=FALSE, warning=FALSE}
num_cols <- data[, sapply(data, is.numeric)]
num_cols <- na.omit(num_cols)
cort <- cor(num_cols)
```

# Exploratory analysis

* In MS1, we performed exploratory data analysis (EDA) for all the predictors in the dataset. Based on the insights we gained from the EDA, we can now build a more effective and informed linear mixed model in MS2.

# Data corealtion plot
```{r echo=FALSE,fig.height=20, fig.width=20}
corrplot::corrplot(cort,order="FPC",type="lower",diag = T,method = "square", addCoef.col = "red")
```

* MD - PD and ATP - RTP are highly correlated, so we should consider only one among each of them.

* We consider MD and ATP.

\newpage
```{r include=FALSE}
data$Day.<- as.factor(data$Day.)
data$Day_Type <- as.factor(data$Day_Type)
data$Gender <- as.factor(data$Gender)
data$Trip_Period <- as.factor(data$Trip_Period)
data$Day. <- as.factor(data$Day.)
```

```{r include=FALSE}
Df_rlevel <- within(data, Day_Type<- relevel(Day_Type, ref = "WeekEnd") )
Df_rlevel <- within(Df_rlevel, Gender<- relevel(Gender, ref = "Female") )
Df_rlevel <- within(Df_rlevel, Trip_Period<- relevel(Trip_Period, ref = "Morning") )
```

\newpage
# HR_Raw Full model
```{r echo=TRUE}
full <- lmer(HR_Raw.mean ~ 1 + Weather.mean + JF.mean +Speed.mean +ATP.mean +
               Accel_Energy.mean + Rot_Energy.mean  + State_Anxiety.mean + 
               B5A.mean + B5E.mean + B5N.mean + B5O.mean + MD.mean + 
               TD.mean + P.mean + E.mean + F.mean + Trip_Period + Day_Type +
               Trait_Anxiety.mean + B5C.mean + Gender + (1|P_ID), 
              data = Df_rlevel, REML=FALSE)

```

```{r echo=FALSE}
full_model_summary<-summary(full) 
```

## Full model summary
```{r}
full_model_summary
```

## Full Model AIC
```{r include=FALSE}
aic.full.model<- AIC(full)
```

```{r}
aic.full.model 
```


\newpage
## Full model Plots
```{r,include=FALSE, warning=FALSE}

levels = c("A", "B", "C", "D")
num = c(5, 10, 15, 20)
ymin = c(0, 0, 0, 0)
ymax = c(1, 2, 3, 4)

Legend_DF = data.frame(levels, num, ymin, ymax)

plot <- ggplot(Legend_DF, aes(x = levels, y = num, colour = levels)) +
  geom_errorbar(aes(ymin = ymin, ymax = ymax), size = 1.1) +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    axis.text.x = element_text(face = "bold", size = 10),
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.title = element_blank(),
    legend.key.width = unit(2, 'cm'),
    legend.text = element_text(size = 20)
  ) +
  theme(axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank()) +
  scale_color_manual(
    values = c("black","steelblue", "orange", "red"),
    #values = c("black", "orange", "red"),
    breaks = c("A", "B", "C", "D"),
    labels = c("     ","*     ", "**     ", "***")
  ) 
# print(plot)

mylegend = get_legend(plot)
```

```{r include=FALSE, warning=FALSE}

# Trip_Period
tp<-plot_model(full, 
             type = "pred", 
             terms = "Trip_Period",
             dot.size = 6,
             line.size = 2,
             title = "Trip_Period") +  theme_bw()+
    aes(color = c("1", "2")) +
    scale_color_manual( values = c( "gray","red")) +
      theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold"),
        legend.position = "none"
        )+ labs(x="", y="")

# Day_Type
dt <- plot_model(full,
             type = "pred", 
             terms = "Day_Type",
             dot.size = 6,
             line.size = 2,
             title = "Day_Type")  + 
  aes(color = "Day_Type") +  theme_bw()+
    aes(color = c("1", "2")) +
    scale_color_manual( values = c( "gray","steelblue")) +
      theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold"),
        legend.position = "none"
        )+ labs(x="", y="")

# Weather
wt <- plot_model(full,
             type = "pred", 
             terms = "Weather.mean",
             dot.size = 6,
             line.size = 2,
             title = "Weather.mean")  + 
  aes(color = "Weather.mean") +
  scale_color_manual(values = "black") +
  geom_vline(
    xintercept = mean(Df_rlevel$Weather.mean),
    linetype = "dashed",
    color = "gray",
    size = 1
  )+  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold"),
        legend.position = "none"
        )+ labs(x="", y="")


# Jam Factor
jf <- plot_model(full,
             type = "pred", 
             terms = "JF.mean",
             dot.size = 6,
             line.size = 2,
             title = "JF.mean")  + 
  aes(color = "JF.mean") +
  scale_color_manual(values = "black") +
  geom_vline(
    xintercept = mean(Df_rlevel$JF.mean,na.rm=T),
    linetype = "dashed",
    color = "gray",
    size = 1
  )+  theme_bw()+
  theme(panel.grid = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold"),
        legend.position = "none"
        )+ labs(x="", y="")




# Trait_Anxiety.mean
ta <- plot_model(full, 
             type = "pred", 
             terms = "Trait_Anxiety.mean",
             dot.size = 6,
             line.size = 2,
             title = "Trait_Anxiety.mean")+ 
        aes(color = "Trait_Anxiety.mean") +
        scale_color_manual(values = "orange") +
        geom_vline(
          xintercept = mean(Df_rlevel$Trait_Anxiety.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# Speed.mean
speed<-plot_model(full, 
             type = "pred", 
             terms = "Speed.mean",
             dot.size = 6,
             line.size = 2,
             title = "Speed.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$Speed.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")


# ATP.mean
atp<-plot_model(full, 
             type = "pred", 
             terms = "ATP.mean",
             dot.size = 6,
             line.size = 2,
             title = "ATP.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$ATP.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")


# Accel_Energy.mean
ae<-plot_model(full, 
             type = "pred", 
             terms = "Accel_Energy.mean",
             dot.size = 6,
             line.size = 2,
             title = "Accel_Energy.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$Accel_Energy.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")


# Rot_Energy.mean
re<-plot_model(full, 
             type = "pred", 
             terms = "Rot_Energy.mean",
             dot.size = 6,
             line.size = 2,
             title = "Rot_Energy.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$Rot_Energy.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

#State_Anxiety.mean
sa<-plot_model(full, 
             type = "pred", 
             terms = "State_Anxiety.mean",
             dot.size = 6,
             line.size = 2,
             title = "State_Anxiety.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$State_Anxiety.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# B5A.mean
B5A<-plot_model(full, 
             type = "pred", 
             terms = "B5A.mean",
             dot.size = 6,
             line.size = 2,
             title = "B5A.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$B5A.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# B5C.mean
B5C<-plot_model(full, 
             type = "pred", 
             terms = "B5C.mean",
             dot.size = 6,
             line.size = 2,
             title = "B5C.mean")+ 
        aes(color = "B5C.mean") +
        scale_color_manual(values = "orange") +
        geom_vline(
          xintercept = mean(Df_rlevel$B5C.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# B5E.mean
B5E<-plot_model(full, 
             type = "pred", 
             terms = "B5E.mean",
             dot.size = 6,
             line.size = 2,
             title = "B5E.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$B5E.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# B5N.mean
B5N<-plot_model(full, 
             type = "pred", 
             terms = "B5N.mean",
             dot.size = 6,
             line.size = 2,
             title = "B5N.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$B5N.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# B5O.mean
B5O<-plot_model(full, 
             type = "pred", 
             terms = "B5O.mean",
             dot.size = 6,
             line.size = 2,
             title = "B5O.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$B5O.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# Gender
Gender<-plot_model(full, 
             type = "pred", 
             terms = "Gender",
             dot.size = 6,
             line.size = 2,
             title = "Gender")+ 
        aes(color = "Gender") +  theme_bw()+
    aes(color = c("1", "2")) +
    scale_color_manual( values = c( "gray","red")) +
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# MD.mean
MD<-plot_model(full, 
             type = "pred", 
             terms = "MD.mean",
             dot.size = 6,
             line.size = 2,
             title = "MD.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$MD.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# TD.mean
TD<-plot_model(full, 
             type = "pred", 
             terms = "TD.mean",
             dot.size = 6,
             line.size = 2,
             title = "TD.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$TD.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# P.mean
P<-plot_model(full, 
             type = "pred", 
             terms = "P.mean",
             dot.size = 6,
             line.size = 2,
             title = "P.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$P.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# E.mean
E<-plot_model(full, 
             type = "pred", 
             terms = "E.mean",
             dot.size = 6,
             line.size = 2,
             title = "E.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$E.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# F.mean
Fm<-plot_model(full, 
             type = "pred", 
             terms = "F.mean",
             dot.size = 6,
             line.size = 2,
             title = "F.mean")+ 
        geom_vline(
          xintercept = mean(Df_rlevel$F.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")
```

```{r include=FALSE, warning=FALSE, fig.height=20, fig.width=15}

full.final <- ggarrange(tp, dt,Gender,ta,B5C, wt,jf,speed,atp,ae,re,sa,B5A,B5E,B5N,B5O,MD,TD,P,E,Fm, ncol = 3, nrow=7)

withLegend = cowplot::plot_grid(full.final,mylegend, nrow=2,rel_heights = c(.9,.1))
withLegend
```



```{r echo=FALSE, fig.height=20, fig.width=15}
# Add a title to the entire grid of plots
title_plot <- ggplot() + 
  theme_void() + 
  labs(title = "Predictor Plot") +
  theme(plot.title = element_text(size = 25, vjust = -10))

# Combine the title plot and the grid of plots
final_plot <- cowplot::plot_grid(title_plot, withLegend, nrow = 2, rel_heights = c(0.1, 1))

# Display the final plot
final_plot
```


\newpage

```{r echo=FALSE, fig.height=8}

sjPlot::plot_model(full, type = "re",
                   show.values=TRUE, show.p=TRUE) + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
          axis.text = element_text(size = 15)
       ) + theme_bw()
```

\newpage

```{r echo=FALSE, fig.height=8}

sjPlot::plot_model(full,
                   show.values=TRUE, show.p=TRUE) + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
          axis.text = element_text(size = 20)
       ) + theme_bw()
```


\newpage
# Backward Elimination (BE)
## BE steps

```{r echo=FALSE}
step_bw <- step(full, direction = "backward")
```

```{r}
step_bw
```



```{r include=FALSE, message=FALSE, warning=FALSE}

bw.mod <- get_model(step_bw)

suggested_bw <- bw.mod@call
suggested_bw_model <- eval(suggested_bw)

suggested_bw_model_summary <- summary(suggested_bw_model)
```


## BE summary

```{r}
suggested_bw_model_summary
```

## BE AIC

```{r include=FALSE}
aic.backward<- AIC(suggested_bw_model)
```

```{r}
aic.backward
```

\newpage

# Forward Elimination (FE)
## FE steps

```{r echo=FALSE, warning=FALSE}

#define intercept-only model
intercept_only <- lmer(HR_Raw.mean ~ 1 + (1|P_ID), data=Df_rlevel)

step_fw <- step(intercept_only, scope=formula(full), direction = "forward")

```

```{r}
step_fw
```


```{r include=FALSE, message=FALSE, warning=FALSE}
fw_mod <- get_model(step_fw)

suggested_fw_model <- eval(fw_mod@call)

suggested_fw_model_summary <- summary(suggested_fw_model)
```
## FE summary
```{r}
suggested_fw_model_summary
```

## FE AIC
```{r include=FALSE}
aic.forward<- AIC(suggested_fw_model)
```

```{r}
aic.forward
```


\newpage
# Both Direction Elimination (BDE)
## BDE steps

```{r echo=FALSE, warning=FALSE}

#define intercept-only model
intercept_only <- lmer(HR_Raw.mean ~ 1 + (1|P_ID), data=Df_rlevel)

step_bd <- step(intercept_only, scope=formula(full), direction = "both")

```

```{r}
step_bd
```


```{r include=FALSE, message=FALSE, warning=FALSE}
bd_mod <- get_model(step_bd)

suggested_bd_model <- eval(bd_mod@call)

suggested_bd_model_summary <- summary(suggested_bd_model)
```
## BE summary
```{r}
suggested_bd_model_summary
```

## BE AIC
```{r include=FALSE}
aic.both<- AIC(suggested_bd_model)
```

```{r}
aic.both
```


\newpage
# Optimal model

* Backward elimiantion model is suggested one as it has low AIC value compared to Forward elimiantion and Both Direction elimiantion.

## Optimal model summary
```{r}
suggested_bw_model_summary
```

## Optimal model plots
## Predictor plot
```{r include=FALSE, warning=FALSE}

# Trip_Period
tp<-plot_model(suggested_bw_model, 
             type = "pred", 
             terms = "Trip_Period",
             dot.size = 6,
             line.size = 2,
             title = "Trip_Period") +  theme_bw()+
    aes(color = c("1", "2")) +
    scale_color_manual( values = c( "gray","red")) +
      theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold"),
        legend.position = "none"
        )+ labs(x="", y="")

# Day_Type
dt <- plot_model(suggested_bw_model,
             type = "pred", 
             terms = "Day_Type",
             dot.size = 6,
             line.size = 2,
             title = "Day_Type")  + 
  aes(color = "Day_Type") +  theme_bw()+
    aes(color = c("1", "2")) +
    scale_color_manual( values = c( "gray","steelblue")) +
      theme(panel.grid = element_blank(),
        plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(size = 10, face = "bold"),
        axis.text.y = element_text(size = 10, face = "bold"),
        legend.position = "none"
        )+ labs(x="", y="")



# Trait_Anxiety.mean
ta <- plot_model(suggested_bw_model, 
             type = "pred", 
             terms = "Trait_Anxiety.mean",
             dot.size = 6,
             line.size = 2,
             title = "Trait_Anxiety.mean")+ 
        aes(color = "Trait_Anxiety.mean") +
        scale_color_manual(values = "red") +
        geom_vline(
          xintercept = mean(Df_rlevel$Trait_Anxiety.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# Speed.mean
speed<-plot_model(suggested_bw_model, 
             type = "pred", 
             terms = "Speed.mean",
             dot.size = 6,
             line.size = 2,
             title = "Speed.mean")+ 
        aes(color = "Speed.mean") +
        scale_color_manual(values = "steelblue") +
        geom_vline(
          xintercept = mean(Df_rlevel$Speed.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")


# B5C.mean
B5C<-plot_model(suggested_bw_model, 
             type = "pred", 
             terms = "B5C.mean",
             dot.size = 6,
             line.size = 2,
             title = "B5C.mean")+ 
        aes(color = "B5C.mean") +
        scale_color_manual(values = "orange") +
        geom_vline(
          xintercept = mean(Df_rlevel$B5C.mean),
          linetype = "dashed",
          color = "gray",
          size = 1
        )+  theme_bw()+
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")

# Gender
Gender<-plot_model(suggested_bw_model, 
             type = "pred", 
             terms = "Gender",
             dot.size = 6,
             line.size = 2,
             title = "Gender")+ 
        aes(color = "Gender") +  theme_bw()+
    aes(color = c("1", "2")) +
    scale_color_manual( values = c( "gray","red")) +
        theme(panel.grid = element_blank(),
              axis.title.y = element_blank(),
              plot.title = element_text(hjust = 0.5), 
              axis.text.x = element_text(size = 10, face = "bold"),
              axis.text.y = element_text(size = 10, face = "bold"),
              legend.position = "none"
              )+ labs(x="", y="")


```

```{r echo=FALSE, warning=FALSE, fig.height=10, fig.width=15}
opt.final <- ggarrange(tp,dt,Gender,ta,B5C,speed, ncol = 3, nrow=2)

withLegend = cowplot::plot_grid(opt.final,mylegend, nrow=2,rel_heights = c(.9,.1))
withLegend
```

\newpage

```{r echo=FALSE, fig.height=8}

sjPlot::plot_model(suggested_bw_model, type = "re",
                   show.values=TRUE, show.p=TRUE) + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
          axis.text = element_text(size = 15)
       ) + theme_bw()
```

\newpage

```{r echo=FALSE}

sjPlot::plot_model(suggested_bw_model,
                   show.values=TRUE, show.p=TRUE) + 
  theme(plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
          axis.text = element_text(size = 10)
       ) + theme_bw()
```

# Conclusion
* The final predictors that effect the HR_Raw are Speed.mean, Trip_PeriodAfternoon, Day_TypeWeekDays, Trait_Anxiety.mean, B5C.mean and GenderMale.